### 2023-03-30 resilience-safe-down.tex
up

\begin{proof}

\end{proof}

>>>>

\begin{proof}
Downward compatibility of $\mathscr{S}=(S,\rightarrow, \leq)$ 
means that
for all $s_1, s_2, t_1 \in S$ with
$s_2 \leq s_1$ and $s_1 \to t_1$
there
exists
$t_2 \leq t_1$ such that $s_2 \to^* t_2$.

Let $D$ be a downward-closed subset of $S$
and let $x \in \downarrow \pred^*(D)$.
By design there exists
$y \in \pred^*(D)$ 
such that $x \leq y$
and $d \in D$ such that
$y \to a_1 \to a_2 \to \cdots \to a_m \to d$.

By downward compatibility

$y \to a_1$

implies

$x \to^* a'_1$

with 
$a'_1 \leq a_1$.

Then

$a_i \to a_{i+1}$

implies the existence of $a'_{i+1} \leq a_{i+1}$ such that

$a'_i \to^* a'_{i+1}$,

and by induction

 $x \to^* a'_1 \to^* \cdots \to^* a'_{m} \to^* d'$

where

$d' \leq d$ belongs to $D$ by downward closure of $D$.

Hence $x \in \pred^*(D)$.
\end{proof}
